GVN-Hoist: Hoisting Computations from Branches

### 2016-08-14 hoist.tex
math

In this program the computations of tmax and tmin are identical to the
computations of tmin and tmax of sibling branch respectively. Both tmax and tmin
depends on inv which depends on a division operation which is generally more
expensive than the addition, subtraction and multiplication operations. The
total latency of computation across each branch is:

O(div) + 2(O(sub) + O(mul))
Or for out of order processors with two add units and two multiply units:
O(div) + O(sub) + O(mul)

@@

In this code the two subtractions and the division operations can be executed in
parallel because there are no dependencies among them. So the total number of
cycles will be max(O(div), O(sub)) + O(mul) = O(div) + O(mul); since O(div) is
usually much greater than O(sub) \cite{x86,aarch64}

>>>>

In this program the computations of tmax and tmin are identical to the
computations of tmin and tmax of sibling branch respectively. Both tmax and tmin
depends on inv which depends on a division operation which is generally more
expensive than the addition, subtraction and multiplication operations. The
total latency of computation across each branch is:
$O(div) + 2(O(sub) + O(mul))$
Or, for out of order processors with two add units and two multiply units:
$O(div) + O(sub) + O(mul)$

@@

In this code the two subtractions and the division operations can be executed in
parallel because there are no dependencies among them. So the total number of
cycles will be $max(O(div), O(sub)) + O(mul) = O(div) + O(mul)$; since $O(div)$ is
usually much greater than $O(sub)$ \cite{x86,aarch64}
